What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-02 paper/main.tex
minor edit to sec 6

We quantify the usability and performance of \tool by compiling an extensive set of \ltl\ formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of all real-life \ltl\ formulas over those metrics. We release the set of real-life \ltl\ formulas as a benchmark set for the research community. Our experimental evaluation conclusively demonstrates that \tool scales to provide helpful visualizations of \ltl\ formulas written by humans.

>>>>

We quantify the usability and performance of \tool by compiling an extensive set of \ltl\ formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of real-life \ltl\ formulas over those metrics.
% We release the set of real-life \ltl\ formulas as a benchmark set for the research community. 
Our experimental evaluation conclusively demonstrates that \tool scales to provide helpful visualizations of \ltl\ formulas written by humans.
